Explorations to Optimize the Parareal Algorithm \\to Solve ODEs in Given Applications

### 2014-12-10 paper.tex
small change in paper typo

@@

For the speaker problem, we designed a problem-specific method to parallelize in space and divide Pierce Hall into subsections such that each processor would receive a division of the building to compute. We wish to strong scaling, in which the computation time of our parallel method will decrease as we increase the number of processors. We compare this version to the serial version we did for Homework 4.

>>>>

\subsection{Visualization of Parareal Scheme}

\begin{figure}[H]
\begin{center}
\includegraphics[width=0.75\linewidth]{parareal_visualization.png}
\caption{Graphical representation of the parareal scheme.}
\label{fig:pararealvis}
\end{center}
\end{figure}

@@

For the speaker problem, we designed a problem-specific method to parallelize in space and divide Pierce Hall into subsections such that each processor would receive a division of the building to compute. We wish to show strong scaling, in which the computation time of our parallel method will decrease as we increase the number of processors. We compare this version to the serial version we did for Homework 4.
